Nail: A practical interface generator for data formats

### 2014-05-02 paper/osdi14/design.tex
Goals motivated by bugs

Nail's goals are to reduce programmer effort required to safely interact
with data formats.  In particular, this means:

@@

\item Using the grammar to define both the \emph{external format}
      and the \emph{internal representation}.

\item Both parsing inputs into internal representations, as well as
      generating outputs from internal representations, without
      requiring the programmer to write any semantic actions.

\item Eliminating redundancy in internal representations, such as
      storing both an explicit length field and an implicit length
      of a container data structure, to provide programmers
      an unambiguous view of the data.

>>>>

Nail's goals are to reduce programmer effort required to safely interact with data formats and
prevent vulnerabilities like those described in \S\ref{s:motivation}. In particular, this means:

@@

\item Using the grammar to define both the \emph{external format} and the \emph{internal
    representation}, allowing the same grammar to be re-used in multiple applications, avoiding
  vulnerabilities like the Android Master Key.

\item Both parsing inputs into internal representations, as well as
      generating outputs from internal representations, without
      requiring the programmer to write any semantic actions. This prevents
      vulnerabilities such as the XNU bug, where format recognition and data processing
      are mixed and interact in unexpected ways.

\item Eliminating redundancy in internal representations, such as
      storing both an explicit length field and an implicit length
      of a container data structure, to provide programmers
      an unambiguous view of the data, to avoid bugs such as in the Python ZIP library.
